Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-20 article.tex
Ajout critères améliorés

\subsubsection{Quadrant criterion}
\begin{figure}[!b]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}}
    \caption{Example of a Delaunay triangulation}
    \label{fig:crit_qua}
\end{figure}

As introduced in a previous article \cite{10201211} its goal is to prevent all potential neighbours to be in the same angle range. Therefore, it was mainly thought to be used with the 
$k$-NN potential neigbours method.

@@

\subsubsection{$3$-NN mean distance}
For each base station $i$, the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in 
$\unit{km}$). According to the value of $\gamma_i$, the base station can either be classified as part of one of the categroies of 
Table~\ref{table:crit_summary}:
\begin{itemize}
    \item city center: $\gamma_i\in [0,1]$;
    \item urban area: $\gamma_i\in ]1,2]$;
    \item extra-urban: $\gamma_i\in ]2,4]$;
    \item countryside: $\gamma_i\in ]4,\infty[$.
\end{itemize}

To make this method work properly, only \acrshort{bs} from the same provider have to be kept into the calculation process.

Althought, this values are working well on France, we haven't tried yet on another country.

\subsection{Improvement of filtering criteria}

\begin{table}[!b]
    \centering
    \caption{Summary of criteria values}
    \label{table:crit_summary}
    \begin{tabular}{lcc}
        \toprule
        \textbf{Description} & \textbf{\emph{max\_distance}} & \textbf{\emph{min\_angle}} \\
        \cmidrule(lr){1-3}
        city center & $\unit[2]{km}$ & $5^\circ$ \\
        urban area & $\unit[5]{km}$ & $10^\circ$ \\
        extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
        countryside & $\unit[15]{km}$ & $20^\circ$ \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/points.png}}
    \caption{Example of a Delaunay triangulation}
    \label{fig:crit_pts}
\end{figure}

\begin{figure}[!b]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/distance_elim.png}}
    \caption{Example of a Delaunay triangulation}
    \label{fig:crit_dis}
\end{figure}

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/angle_elim.png}}
    \caption{Example of a Delaunay triangulation}
    \label{fig:crit_ang}
\end{figure}

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/neighs.png}}
    \caption{Example of a Delaunay triangulation}
    \label{fig:crit_nei}
\end{figure}

\subsubsection{Distance criterion}
When looking at the results of Delaunay triangulation, we realise that some edges, mostly on the border of $P$ are too long.

Indeed, a \acrshort{bs} does not have an infinite coverage area. As a consequence, for each \acrshort{bs} the neighbouring connexions that are longer than a certain value, called \emph{max\_distance} (cf. Table~\ref{table:crit_summary}), are suppressed.

Therefore, the connexion between $p$ and $r$ needs to be suppressed. How? The angle $\widehat{qrp}$ is calculated and if it is narrower than a certain value, called \emph{min\_angle} (cf. Table~\ref{table:crit_summary}), the longest edge is suppressed.

[Dire que c'est des angles adjacents]

It consists in dividing the space around each base station into quadrants and keeping only a certain number of potential neighbours
in each of the quadrants. The number of quadrants has been fixed to six \cite{art_del_paq}.

The criterion has been upgraded by adding the possibility to rotate the quadrants. The offset angle selected, which is between $0$ and 
$60$ degrees, is the one that maximises the sum of the distances of the potential neighbours to their closest quadrant delimitation.

@@

The quadrant criterion is illustrated in Fig~\ref{fig:crit_qua}.

>>>>

@@

\subsubsection{$3$-NN mean distance}
For each base station $i$, the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in 
$\unit{km}$). According to the value of $\gamma_i$, the base station can either be classified into one of these categories:
\begin{itemize}
    \item city center: $\gamma_i\in [0,1]$;
    \item urban area: $\gamma_i\in ]1,2]$;
    \item extra-urban: $\gamma_i\in ]2,4]$;
    \item countryside: $\gamma_i\in ]4,\infty[$.
\end{itemize}
If you want this method to work properly, only \acrshort{bs} from the same provider have to be kept into the calculation process.
Althought this values are working well on France, we haven't tried yet on another country.

\subsection{Improvement of filtering criteria}
\begin{table}[!t]
    \centering
    \caption{Summary of criteria values}
    \label{table:crit_summary}
    \begin{tabular}{lcc}
        \toprule
        \textbf{Description} & \textbf{\emph{max\_distance}} & \textbf{\emph{min\_angle}} \\
        \cmidrule(lr){1-3}
        city center & $\unit[2]{km}$ & $5^\circ$ \\
        urban area & $\unit[5]{km}$ & $10^\circ$ \\
        extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
        countryside & $\unit[15]{km}$ & $20^\circ$ \\
        \bottomrule
    \end{tabular}
\end{table}

\subsubsection{Distance and angle criterion}
As seen in section~\ref{sec:reminder}, after having found potential neighbours for each base station,
we need to filtrate this connexions. However, this applies the same distance and angle threshold for all base stations, without taking in account the difference of density.

The method we propose now is to take in account those differences of density for each site to apply a different thresholdn according to the category the site in classified in.

You can find those values listed in Table~\ref{table:crit_summary}.

\subsubsection{Quadrant criterion}
This criterion has been upgraded by adding the possibility to rotate the quadrants. The offset angle selected, which is between $0$ and 
$60$ degrees, is the one that maximises the sum of the distances of the potential neighbours to their closest quadrant delimitation.

@@

The quadrant criterion is illustrated in Fig~\ref{fig:crit_qua}.
\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}}
    \caption{Illustation of the rotated quadrant criterion}
    \label{fig:crit_qua}
\end{figure}
